---
title: Benchmark Neural Predictability of G-factor
author: Liang Zhang
date: 2023-05-10
draft: false
format:
  revealjs:
    code-fold: false
execute:
  warning: false
  message: false
bibliography: references.bib
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
source(here::here("R/constants.R"))
store_modality_comparison <- targets::tar_config_get(
  "store", 
  config = here::here("_targets.yaml"),
  project = "project_modality_comparison"
)
```

# FMRI Sample Description

```{r}
#| label: describe-sample
#| results: asis

targets::tar_load(
  c(subjs_info_clean, subjs_combined),
  store = here::here(store_modality_comparison)
)
subjs_info_clean |> 
  filter(sub_id %in% subjs_combined) |> 
  report::report_participants() |> 
  cat()
```

# Compare CPM among different modalities

## Configurations {.smaller}

Parameters are as follows (mainly inspired by @greene2018):

-   FMRI data pre-processing: `with` or `without` global signal regression (GSR)
-   Node parcellation: Power's *264* nodes (`Power264`) or Shen's *268* nodes (`nn268`)
-   Modality:
    -   `task`: N-back task
    -   `rest`: resting-state
    -   `combined`: combines N-back and rest-stating by appending these two data
-   Edge selection threshold method: correlation p.value based (`alpha`) or network sparsity based (`sparsity`)

```{r}
#| label: render-results-modality
#| results: asis

targets::tar_load(cpm_pred, store = here::here(store_modality_comparison))
config <- distinct(cpm_pred, parcel, gsr)
for (row in seq_len(nrow(config))) {
  knitr::knit_expand(
    here::here("template/modality_comparison_tmpl.qmd"),
    parcel = config$parcel[[row]],
    gsr = config$gsr[[row]]
  ) |>
    knitr::knit(text = _, quiet = TRUE) |>
    cat()
  cat("\n\n")
}
```

# Compare between gender/sex

```{r}
#| label: render-results-sex
#| results: asis

targets::tar_load(cpm_pred_sex, store = here::here(store_modality_comparison))
config <- distinct(cpm_pred_sex, parcel, gsr)
for (row in seq_len(nrow(config))) {
  knitr::knit_expand(
    here::here("template/sex_comparison_tmpl.qmd"),
    parcel = config$parcel[[row]],
    gsr = config$gsr[[row]]
  ) |>
    knitr::knit(text = _, quiet = TRUE) |>
    cat()
  cat("\n\n")
}
```

# References
